Price of Anarchy for Mean Field Games

### 2018-07-20 PoA.tex
minor edits

We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation}
		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

@@

	%Nicolas: Mean Value theorem
	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$. Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
	\begin{IEEEeqnarray}{rCl}
		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{\bar{b}_2,MFG} )^2  \cdot T \nonumber \\
		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2)} \right)^2,
		\label{eq:delta_SC_b_2_bar_infty}
	\end{IEEEeqnarray}
	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $f(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$. Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $. Then there exists $\bar{b}_2^* := \bar{b}_2^*(c_{b_2},t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < c_{b_2}$. Then $f(\bar{b}_2,t_2) - c_3 + 2c_{b_2} > c_{b_2}$ and 
	\begin{equation*}
	\begin{array}{rl}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
		& \leq  e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{**}>\bar{b}_2^{*}$, such that for all $\bar{b}_2>\bar{b}_2^{**}$, we have:
	\begin{equation}
	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }|<\epsilon.
	\label{eq:limit_p_f(p)}
	\end{equation}

 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$. Given $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$. Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce:
 	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
 	$$

@@

	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
	Thus, by taking $\epsilon \to 0$, we have:
	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$

% error in the proof of proposition 5
\begin{comment}

	%Thus, for $t \in [0,T)$, we have:
	%\begin{equation*}
	%B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
	%\end{equation*}
	%From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
	%$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$

>>>>

We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. Note that under the above conditions, we have $\delta^-_u<0<\delta^+_u$ and thus, $u_t \geq 0$ for all $t\in[0,T]$. We have analogous expressions for $w_t$ and $\eta_t$, which are also nonnegative, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$, and the above conditions on the parameters $B$, $C^u$, $D^u$, $C^w$, $D^w$, $B^\eta$, $C^\eta$, and $D^\eta$ are exactly the conditions in assumption (\ref{eq:assumptions}).

@@

	% modification Main point 5 (nicolas)
	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
	\begin{equation}
		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
	\end{equation}
	Then we have:
	\begin{equation*}
	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
	\end{equation*}
	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

@@

	%Nicolas: Mean Value theorem
	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$. Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
	\begin{IEEEeqnarray}{rCl}
		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{\bar{b}_2,MFG} )^2  \cdot T \nonumber \\
		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2)} \right)^2,
		\label{eq:delta_SC_b_2_bar_infty}
	\end{IEEEeqnarray}
	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$. Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $. Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\vert h(\bar{b}_2) - c_3 \vert < c_{b_2}$. Then $h(\bar{b}_2) - c_3 + 2c_{b_2} > c_{b_2}$ and 
	\begin{equation*}
	\begin{array}{rl}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (h(\bar{b}_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
		& \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{*,2}>\bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$, we have:
	\begin{equation}
	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }|<\epsilon.
	\label{eq:limit_p_f(p)}
	\end{equation}

 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$. Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} > 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$. Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we deduce:
 	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
 	$$

@@

	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 > \bar{b}_2^*$ we have
	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
	Thus, by taking $\epsilon \to 0$, we have:
	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
